Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 robdml.tex
tex

Then, \emph{Hardness Manipulation} (HM) aims to increase the \emph{source} hardness
$H_\mathsf{S}$ into a specified ``\emph{destination} hardness'' $H_\mathsf{D}$,
by finding adversarial examples of the source triplet $(\mA, \mP, \mN)$, \ie,
$(\mA + \hat{\vr}_a, \mP + \hat{\vr}_p, \mN + \hat{\vr}_n)$,
where $(\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n)$ are the adversarial perturbations.
%
If we denote the hardness of the adversarially perturbed \emph{source} triplet
as $\tilde{H}_\mathsf{S}$, the HM can be implemented as follows:
%
\begin{equation}
	%
	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{r_a,r_p,r_n} \big\|\max(0,
	H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \big\|_2^2.
	%
	\label{eq:hm}
	%
\end{equation}

%
Note, it is not expected to lower the hardness during the attack, namely
$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
%
%

\cref{fig:hm}
%
The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_\mathsf{S}>H_\mathsf{D}$,
automatically stopping the optimization.
%
This is because $H_\mathsf{S}$ will be reduced once greater than $H_\mathsf{D}$ in standard Mean
Square Error.
%
The optimization problem can be solved by projected gradient
descent~\cite{madry}.
%
And the resulting adversarial examples are used for adversarially training the
DML model:
%
$L_\text{T}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
\phi(X_n^S+\bar{r}_n))$.

>>>>

Then, \emph{Hardness Manipulation} (HM) aims to increase the \emph{source}
hardness $H_\mathsf{S}$ into a specified ``\emph{destination} hardness''
$H_\mathsf{D}$, by finding adversarial examples of the source triplet $(\mA,
\mP, \mN)$, \ie, $(\mA + {\vr}_a, \mP + {\vr}_p, \mN + {\vr}_n)$, where
$({\vr}_a, {\vr}_p, {\vr}_n)$ are the adversarial perturbations.
%
If we denote the hardness of the adversarially perturbed \emph{source} triplet
as $\tilde{H}_\mathsf{S}$, the HM can be implemented as follows:
%
\begin{equation}
	%
	\hat{\vr}_a, \hat{\vr}_p, \hat{\vr}_n = \argmin_{\vr_a,\vr_p,\vr_n}
	\Big\|\max(0, H_\mathsf{D} - \tilde{H}_\mathsf{S} ) \Big\|_2^2.
	%
	\label{eq:hm}
	%
\end{equation}
%
The $\max(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when
$H_\mathsf{S}>H_\mathsf{D}$, automatically stopping the optimization, because
$H_\mathsf{S}$ is not desired to be reduced once being greater than
$H_\mathsf{D}$.
%
The \cref{eq:hm} is written in the L-$2$ norm form instead of the standard Mean Squared
Error because HM can be directly extended into vector form for a
mini-batch.
%
The optimization problem can be solved by projected gradient
descent~\cite{madry}.
%
And the resulting adversarial examples are used for adversarially training the
DML model:
%
$L_\text{T}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
\phi(X_n^S+\bar{r}_n))$.

\cref{fig:hm}
%
Note, it is not expected to lower the hardness during the attack, namely
$E[H_\mathsf{D}]$ should be greater or equal to $E[H_\mathsf{S}]$.
%
%
